### 2013-03-28 doc/sosp13/overview.tex
new eval. commit to merge
FL

@@

\item [Tasking system.] The tasking system supports lightweight multithreading
to tolerate communication latency and global distributed work-stealing (i.e.,
tasks can be stolen from any node in the system), which provides automated
load balancing. The scheduler oversubscribes to have more worker threads than
required for latency tolerance. By having at least several threads ready to
run at all times, the scheduler can prefetch a context data into cache to
lower the likelihood of costly main memory accesses during a context switch.

@@

% \paragraph{Exploiting Latency Tolerance} As we will show later, Grappa can tolerate latencies way beyond that of the network. Therefore, Grappa can afford to \emph{trade latency for throughput\/}: by {\em increasing\/} latency in key components of the system we are able to increase our aggregate random access bandwidth (by delaying and aggregating messages), our synchronization bandwidth (by delegating operations to remote nodes), and our ability to improve load imbalance (work stealing increases latency).

>>>>

% \TODO{Whats missing before diving into the system
%     is why we think we can build a system with these
%     techniques and it will work well--myers}

@@

\item [Tasking system.] The tasking system supports lightweight multithreading to tolerate communication latency and global distributed work-stealing (i.e., tasks can be stolen from any node in the system), which provides automated load balancing. The scheduler oversubscribes to have more worker threads than required for latency tolerance. By having at least four threads per processor core ready to run at all times, the scheduler can prefetch a worker's state into cache to lower the likelihood of costly main memory accesses during a context switch.

@@

% \paragraph{Exploiting Latency Tolerance} As we will show later, \Grappa can tolerate latencies way beyond that of the network. Therefore, \Grappa can afford to \emph{trade latency for throughput\/}: by {\em increasing\/} latency in key components of the system we are able to increase our aggregate random access bandwidth (by delaying and aggregating messages), our synchronization bandwidth (by delegating operations to remote nodes), and our ability to improve load imbalance (work stealing increases latency).
